% PLEASE USE THIS FILE AS A TEMPLATE FOR THE PUBLICATION 
% Check file IOS-Book-Article.tex
%

\documentclass{IOS-Book-Article}     %[seceqn,secfloat,secthm]
%\usepackage{mathptmx}
%\usepackage[T1]{fontenc}
%\usepackage{times}%
\usepackage{graphicx}
\newtheorem{definition}{Definition}
%
%%%%%%%%%%% Put your definitions here


%%%%%%%%%%% End of definitions
\begin{document}
\begin{frontmatter}          % The preamble begins here.
%
%\pretitle{}
\title{Using legal text in the knowledge base paradigm}
\runningtitle{}
%\subtitle{}

% For one author:
%\author{\fnms{} \snm{}}
%\address{}
%\runningauthor{}
%
% Two or more authors:
\author[A]{\fnms{Marjolein} \snm{Deryck}},
\author[B]{\fnms{Jo} \snm{Devriendt}}
\author[B]{\fnms{Simon} \snm{Marynissen}}
\author[A]{\fnms{Joost} \snm{Vennekens}}
\runningauthor{Deryck M. e.a.}
\address[A]{Department of Computer Science, KU Leuven, Campus De Nayer, Sint-Katelijne Waver, Belgium}
\address[B]{Department of Computer Science, KU Leuven, Leuven, Belgium}
%
\begin{abstract}
The Knowledge Base Paradigm advocates the accumulation of domain knowledge in a formal knowledge base to enable its use for multiple applications.
This practice induces flexibility and agility, as changes in the domain are reflected directly in the knowledge base, without affecting the algorithms that use this information.
Similarly, new ways to use this information can be developed independently of the specific domain and are highly portable.
This paper demonstrates these characteristics with the case of Belgian registration duties. 
The concerned legislation changed considerably mid 2018.  
Models for the former and current legislation are developed with IDP.
They are used in accordance with an interactive user interface for which a new implementation to interactively calculate and highlight relevant information was developed.
\end{abstract}


\begin{keyword}
Knowledge Base Paradigm, automatic configuration, IDP
\end{keyword}

\end{frontmatter}

%%%%%%%%%%% The article body starts:


\input{01_Intro}\\
\input{02_Method}\\
\input{03_Case}\\
\input{04_Related}\\
\input{05_Conclusion}\\


\bibliographystyle{splncs}
{\footnotesize\bibliography{bib.bib}}


%%%%%%%%%%% The bibliography starts:
\begin{thebibliography}{99}

\bibitem{Jansen2016}
Jansen, J., Bogaerts, B., Devriendt, J., Janssens, G.,  Denecker, M. (2016). Relevance for SAT(ID). Proceedings of the Twenty-Fifth International Joint Conference on Artificial Intelligence, 596~-~602.

\bibitem{Denecker2015}
Denecker, M., Brewka, G., Strass, H. (2015). A formal theory of justifications. In 13th International Conference on Logic Programming and Non-monotonic Reasoning (pp. 250–264). Springer.

\bibitem{Denecker93}
Denecker, M., & De Schreye, D. (1993). Justification semantics: a unifying framework for the semantics of logic programs. In Proc. of the Logic Programming and Nonmonotonic Reasoning Workshop (pp. 365–379).

\bibitem{DMN}
OMG: Decision Model and Notation 1.1 (2016
\bibitem{IDP}
 de  Cat,  B.,  Bogaerts,  B.,  Bruynooghe,  M.,  Denecker,  M.:   Predicate  logic  as  a
modelling language: The IDP system.  CoRR
abs/1401.6312
(2014)
\bibitem{Ingmar}
Denecker, M., & De Schreye, D. (1993). Justification semantics: a unifying framework for the semantics of logic programs. In Proc. of the Logic Programming and Nonmonotonic Reasoning Workshop (pp. 365–379).
\bibitem{Marjolein}
Deryck, Marjolein, Hasic, faruk, Vanthienen, jan, & Vennekens, joost. (accepted). A case based inquiry into the decision model and notation (DMN) and the knowledge base (KB) paradigm. Proceedings of RuleML RR 2018, Proceedings of RuleML RR 2018.


\end{thebibliography}
\end{document}

